Evolution of the AGN UV luminosity function from redshift 7.5

### 2018-03-06 Paper/paper.tex
Update

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    model.  The symbols show the best fit parameters with 68\%
    uncertainties from the double power law fits to the data in
    redshift bins.  These points are identical to those in
    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
    2$--$3$) are not shown.  In each panel, the black solid curve
    shows the best fit global model, and the coloured curves show a
    random sample drawn from the global posterior.}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal()
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior. \gk{I still think we should show
      the $-18$ case here.}}
  \label{fig:rhoqso}
\end{figure}

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity_18.pdf}
    \includegraphics[width=0.5\textwidth]{emissivity_21.pdf}
    % gammapi.py -- draw_emissivity() 
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.  For comparison,
    various other published determinations of the 1~Ry emissivity of
    quasars are also shown in both panels of Figure~\ref{fig:e912}.
    The blue curve in these panels shows the AGN 1~Ry emissivity model
    of \citet{2012ApJ...746..125H}, which is very similar to the model
    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
    show the determination from the fits of
    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
    to the 1~Ry emissivity evolution in the fits of
    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
    \citet{2015ApJ...813L...8M}.}
  \label{fig:e912}
\end{figure*}

@@

% Add a table for the best fit parameter values?

@@

\begin{figure*}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{g_18.pdf}
    \includegraphics[width=0.5\textwidth]{g_21.pdf}
    \end{tabular}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. \gk{Two
      problems to be addressed in these plots: (a) there is a
      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
      but because our emissivity diverges at $z>7$, I had a to put an
      arbitrary cut-off; (b) the plots are too messy; we probably
      should show fewer things.}}
  \label{fig:gammapi}
\end{figure*}

>>>>

\begin{figure*}
  \begin{center}
    \includegraphics[width=0.7\textwidth]{evolution_global.pdf}
    % summary_fromFile.py 
  \end{center}
  \caption{Luminosity function parameter evolution in the global
    model.  The symbols show the best fit parameters with 68\%
    uncertainties from the double power law fits to the data in
    redshift bins.  These points are identical to those in
    Figure~\ref{fig:evoln}, except that bins with BOSS qsos ($z\sim
    2$--$3$) are not shown.  In each panel, the black solid curve
    shows the best fit global model, and the coloured curves show a
    random sample drawn from the global posterior. \gk{Cannot see
      best-fit curves.  Add open and closed circles to legend.}}
  \label{fig:evoln_global}
\end{figure*}

\begin{figure}
  \begin{center}
    \includegraphics[width=\columnwidth,keepaspectratio]{rhoqso_withGlobal.pdf}
    % rhoqso.py -- draw_withGlobal()
  \end{center}
  \caption{AGN number density evolution in the global model.  Similar
    to Figure~\ref{fig:evoln_global}, symbols show the best fit
    parameters with 68\% uncertainties from the double power law fits
    to the data in redshift bins.  Black solid curve shows the best
    fit global model, and the coloured curves show a random sample
    drawn from the global posterior. \gk{I still think we should show
      the $-18$ case here.  Mention magnitude limits.  Reduce
      transarency.  Extend plot to at least redshift 7.5.  Increase
      legend handle length to match other figure.}}
  \label{fig:rhoqso}
\end{figure}

\begin{figure}
  \begin{center}
    \begin{tabular}{cc}
    \includegraphics[width=0.5\textwidth]{emissivity.pdf}
    % gammapi.py -- draw_emissivity() 
    \end{tabular}
  \end{center}
  \caption{LyC emissivity of AGN assuming 100\% escape fraction.
    Model luminosity functions are integrated down to $M_{1450}=-18$
    in the left panel and $-20$ in the right panel.  For comparison,
    various other published determinations of the 1~Ry emissivity of
    quasars are also shown in both panels of Figure~\ref{fig:e912}.
    The blue curve in these panels shows the AGN 1~Ry emissivity model
    of \citet{2012ApJ...746..125H}, which is very similar to the model
    of \citet{2007ApJ...654..731H}.  The red symbols with error bars
    show the determination from the fits of
    \citet{2015AA...578A..83G}.  The maroon curve is the published fit
    to the 1~Ry emissivity evolution in the fits of
    \citet{2017MNRAS.466.1160M}.  The green curve is the model of
    \citet{2015ApJ...813L...8M}. \gk{Add uncertainties on these fits,
      perhaps by using emcee.}}
  \label{fig:e912}
\end{figure}

@@

\begin{table}
  \caption{Best-fit luminosity function evolution models.  These
    parameters are defined in Equations XX.  See Section XX for
    further details and the redshift range of validity of these
    models.  Errors indicate one-sigma (68.26\%) uncertainties.  Model
    2 is our preferred model.}
  \label{tab:global}
  \begin{tabular}{lrrr}
    \hline 
    Parameter & Model 1 & Model 2 & Model 3 \\
    \hline
    $c_{0,0}$ & $-7.559^{+0.131}_{-0.139}$ & $-7.084^{+0.136}_{-0.142}$ & $-6.842^{+0.077}_{-0.076}$ \\     
    $c_{0,1}$ & $1.013^{+0.079}_{-0.072}$ & $0.753^{+0.080}_{-0.073}$ & $0.590^{+0.039}_{-0.041}$ \\        
    $c_{0,2}$ & $-0.113^{+0.005}_{-0.005}$ & $-0.096^{+0.004}_{-0.005}$ & $-0.083^{+0.003}_{-0.003}$ \\
    \\
    $c_{1,0}$ & $-17.006^{+0.230}_{-0.243}$ & $-15.423^{+0.263}_{-0.261}$ & $-15.140^{+0.144}_{-0.136}$ \\  
    $c_{1,1}$ & $-5.548^{+0.156}_{-0.143}$ & $-6.725^{+0.156}_{-0.171}$ & $-6.910^{+0.091}_{-0.093}$ \\     
    $c_{1,2}$ & $0.588^{+0.016}_{-0.019}$ & $0.737^{+0.018}_{-0.015}$ & $0.750^{+0.012}_{-0.013}$ \\        
    $c_{1,3}$ & $-0.023^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ & $-0.029^{+0.001}_{-0.001}$ \\
    \\
    $c_{2,0}$ & $-3.246^{+0.121}_{-0.123}$ & $-2.973^{+0.117}_{-0.133}$ & $-2.950^{+0.105}_{-0.097}$ \\     
    $c_{2,1}$ & $-0.250^{+0.048}_{-0.050}$ & $-0.347^{+0.050}_{-0.050}$ & $-0.363^{+0.040}_{-0.043}$ \\
    \\
    $c_{3,0}$ & $-2.350^{+0.051}_{-0.060}$ & $-2.545^{+0.123}_{-0.290}$ & $-1.424^{+0.031}_{-0.031}$ \\     
    $c_{3,1}$ & $0.647^{+0.072}_{-0.060}$ & $1.581^{+0.520}_{-0.264}$ & $-0.111^{+0.010}_{-0.010}$ \\       
    $c_{3,2}$ & $3.857^{+0.092}_{-0.073}$ & $2.102^{+0.450}_{-0.283}$ & --- \\        
    $c_{3,3}$ & $27.534^{+41.364}_{-9.405}$ & $1.965^{+0.461}_{-0.464}$ & --- \\      
    $c_{3,4}$ & $-0.002^{+0.074}_{-0.082}$ & $-0.641^{+0.169}_{-0.154}$ & --- \\      
    \hline 
  \end{tabular}
\end{table}

@@

\begin{figure*}
  \begin{center}
    \includegraphics[scale=0.65]{g.pdf}
  \end{center}
  \caption{AGN contribution to the hydrogen photoionisation rate,
    assuming 100\% escape fraction.  Model luminosity functions are
    integrated down to $M_{1450}=-18$ in the left panel and $-20$ in
    the right panel.  The solid black curve shows the hydrogen
    photoionisate rate in our best-fit global model, and the yellow
    curves show a random sample from the global posterior.  The red
    points with error bars in this figure show the measurements of
    \citet{2013MNRAS.436.1023B}, derived from the Lyman-$\alpha$
    forest, and the orange points show the measurements by
    \citet{2011MNRAS.412.2543C} from quasar proximity zones.  The
    dashed green curve shows the hydrogen photoionisation rate
    evolution in the model of \citet{2012ApJ...746..125H}, while the
    solid green curve shows the contribution of quasars to it. \gk{Two
      problems to be addressed in these plots: (a) there is a
      contribution of $z>7$ qsos to the photoionisation rate at $z<7$
      but because our emissivity diverges at $z>7$, I had a to put an
      arbitrary cut-off; (b) the plots are too messy; we probably
      should show fewer things.}}
  \label{fig:gammapi}
\end{figure*}
